Results Summary

### 2025-02-25 analysis.Rmd
wip

  for (i in seq_along(formulas)) {
    if (method_name %in% c("cbps", "entropy", "bart")) {
      package <- "WeightIt"
      approach <- "ipw"
    } else if (method_name %in% c("twang_gbm")) {
      package <- "twang"
      approach <- "ipw"
    } else if (method_name == "subclass") {
      package <- "MatchIt"
      approach <- "subclassification"
    } else {
      package <- "MatchIt"
      approach <- "match w/ replacement"
    }

    if (method_name == "subclass") {
      # Extract subclass weights
      subclass_weights <- weights(design, type = "sampling")

@@

  if(method_name %in% c("cbps", "entropy", "energy", "bart")) {
    # Weightit methods
    matched_data <- m_data
    weights <- method_result$result$weights
    matched_data$weights <- weights
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~weights, data = matched_data)
  } else if (method_name == "twang_gbm") {
    # For TWANG model with weights
    m_data$twang_att_w <- get.weights(method_result$result, stop.method = "es.mean")
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~twang_att_w, data = m_data)
  } else {
    # For MatchIt methods, use get_matches due to having more Tx than C.
    matched_data <- if(method_name == "subclass_glm") {
      MatchIt::match_data(method_result$result, subclass = 5)
    } else {
      MatchIt::get_matches(method_result$result)
    }
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights=~1)
  }

>>>>

  for (i in seq_along(formulas)) {
    if (method_name %in% c("cbps", "entropy", "bart")) {
      package <- "WeightIt"
      approach <- "ipw"
    } else if (method_name %in% c("twang_gbm")) {
      package <- "twang"
      approach <- "ipw"
    } else if (method_name == "subclass_glm") {
      package <- "MatchIt"
      approach <- "subclassification"
    } else {
      package <- "MatchIt"
      approach <- "match w/ replacement"
    }

    if (method_name == "subclass_glm") {
      # Extract subclass weights
      subclass_weights <- weights(design, type = "sampling")

@@

  if(method_name %in% c("cbps", "entropy", "energy", "bart")) {
    # Weightit methods
    matched_data <- m_data
    weights <- method_result$result$weights
    matched_data$weights <- weights
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~weights, data = matched_data)
  } else if (method_name == "twang_gbm") {
    # For TWANG model with weights
    m_data$twang_att_w <- get.weights(method_result$result, stop.method = "es.mean")
    design <- svydesign(ids = ~e_mrn_deidentified, weights = ~twang_att_w, data = m_data)
  } else if(method_name == "subclass_glm") {
    matched_data <- MatchIt::match_data(method_result$result, subclass = "subclass")
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights=~weights)
    design <- postStratify(design, ~subclass, xtabs(~subclass, data = matched_data))
  }  else {
    matched_data <- MatchIt::get_matches(method_result$result)
    design <- svydesign(ids = ~e_mrn_deidentified, data = matched_data, weights=~1)
  }

### 2025-02-25 results-summary.Rmd
wip

library(dplyr)
library(ggplot2)
library(kableExtra)

# Get results summary from the pipeline; no PHI in here
results <- readRDS("final_results.rds")

>>>>

library(dplyr)
library(ggplot2)
library(kableExtra)
source("settings.R")

# Get results summary from the pipeline; no PHI in here
results <- readRDS(file.path(ps_dir, "ps_results_summary.rds"))
